Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-07 paper/Conclusion.tex

Moving this work towards generating a fully verified MSI implementation
requires a number of small steps. First, the simple transliteration of
descriptions between Bluespec and Coq must be done in a mechanical way.
Second, the compilation of Bluespec to hardware is unverified; to fully trust
the implementation the Bluespec compiler must be verified. Some first steps
have been taken in that direction~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must
extend our notion of correctness to provide some guarantee of
liveness and fairness in handling of requests from processors. We have
initial Coq-based proofs that with finite buffers a local fairness condition
holds for our protocol, but more work is needed.

>>>>

Moving this work towards generating a fully verified MSI implementation
requires a number of small steps. First, the simple transliteration of
descriptions between Bluespec and Coq must be done in a mechanical way.
Second, the compilation of Bluespec to hardware is unverified; to fully trust
the implementation, the Bluespec compiler must be verified. Some first steps
have been taken in that direction~\cite{DBLP:conf/cav/BraibantC13}. Finally, we must
extend our notion of correctness to provide some guarantee of
liveness and fairness in handling of requests from processors. We have
initial Coq-based proofs that with finite buffers a local fairness condition
holds for our protocol, but more work is needed.

### 2014-02-07 paper/Introduction.tex
stuff

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size
as well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best of
our knowledge, the largest system that has been verified using model checking
has only 12 processors~\cite{Chen:2008:VHC:1559300}, in an era when many
observers are predicting mainstream systems with hundreds of processor cores.

@@

\adamc{This might be a good place to include a link to the Coq source code.}

>>>>

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size
as well as complexity of the system that has to be verified; most model-checking
based approaches cannot handle more than one level of hierarchy. To the best of
our knowledge, the largest system that has been verified using model checking
has only 12 processors~\cite{Chen:2008:VHC:1559300}, in an era when many
observers are predicting mainstream systems with hundreds of processor cores.

@@

The Coq source code for the definition of store atomicity and the proof of the
MSI protocol can be found in \url{https://github.com/vmurali/CacheProof}.

%\adamc{This might be a good place to include a link to the Coq source code.}
